Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Project Updates

### 2023-07-12 july18meeting_pres2/may30ccgmeeting.tex
cant add .tiff to latex

	\begin{frame}{Selection of TCGA Cancer Types}
			\begin{columns}
				\begin{column}{0.45\textwidth}
					\includegraphics[width=5cm, height=8cm]{img1.png}
				\end{column}
				\begin{column}{0.5\textwidth}
					\begin{itemize}
						\item There is a lack of healthy tissue RNA-seq samples in the TCGA database (12 cancers with more than 10 pairs in M and F)
					\end{itemize}
				\end{column}
			\end{columns}

		\includegraphics[width=5cm, height=8cm]{img1.png}
	\end{frame}

	\begin{frame}{Creating Pan-Cancer Expression Matrices}
		content...
	\end{frame}

	\begin{frame}{Normalizing Pan-Cancer Expression Matrices}
		content...
	\end{frame}

>>>>

	\begin{frame}{Selection of TCGA Cancer Types}
			\begin{columns}
				\begin{column}{0.45\textwidth}
					\includegraphics[width=5cm, height=8cm]{img3.png}
				\end{column}
				\begin{column}{0.5\textwidth}
					\begin{itemize}
						\item There is a lack of healthy tissue RNA-seq samples in the TCGA database (12 cancers with more than 10 pairs in M and F)
						\item Raw count pan-cancer matrices created with 12 remaining TCGA cancer types (BLCA, COAD, ESCA, HNSC, KICH, KIRC, KIRP, LIHC, LUAD, LUSC, STAD, THCA)
					\end{itemize}
				\end{column}
			\end{columns}			
	\end{frame}

	\begin{frame}{Creating and Pre-Filtering Pan-Cancer Expression Matrices}
		\begin{itemize}
			\item For each gene, if expression is $>$ 90th quantile of overall expression in AT LEAST 1 sample, we keep it, otherwise we filter it out
		\end{itemize}
	\end{frame}

	\begin{frame}{Normalizing Pan-Cancer Expression Matrices}
		\includegraphics{all_cancers-M_before_and_after_normalization_v.tiff}
	\end{frame}
